
%
% Conference Papers (The following all requires checking)
%

@inproceedings{ agrawal-hippocratic,
  author = "Rakesh Agrawal and Jerry Kiernan and Ramakrishnan Srikant and Yirong Xu",
  title = "Hippocratic Databases",
  booktitle = "28th Int'l Conf. on Very Large Databases (VLDB), Hong Kong",
  year = "2002",
  url = "citeseer.nj.nec.com/532601.html" }


@inproceedings{Cobena2002,
    title=          "Detecting Changes in XML Documents",
    booktitle=      "Proc. of the International Conference on Data Engineering",
    author=         "Gregory Cobena, Serge Abiteboul, Amelie Marian",
    address=        "San Jose, California, USA",
    month=          feb,
    year=           2002
}


@INBOOK{Jajodia97,
  AUTHOR =       "Sushil Jajodia",
  TITLE =        "The Computer Science and Engineering Handbook 1997",
  CHAPTER =      "49. Database Security",
  pages =        "1112-1124",
  PUBLISHER =    "CRC Press, Inc.",
  YEAR =         "1997"
}

@inproceedings{W3SCHOOLS,
    author = "W3Schools.com",
    title = "W3Schools Online Web Tutorials",
    address = "http://www.w3schools.com/"
}

@inproceedings{PRIVACYORG,
    author = "Privacy.org",
    title = "Privacy.org - The Source for news, Information, and Action",
    address = "http://www.privacy.org/"
}


@inproceedings{LKhan2002,
    title=          "Change Detection of XML Documents Using Signatures",
    booktitle=      "Proc. of International Workshop Real World RDF and Semantic Web Applications",
    author=         "L. Khan, L. Wang, Y. Rao",
    address=        "Hawaii",
    month=          may,
    year=           2002
}



@inproceedings{XYLEME,
    author = "Xyleme Project",
    title = "W3Schools Online Web Tutorials",
    address = "http://www.w3schools.com/"
}


@inproceedings{YWang,
    title=          "Detecting Changes in XML Documents",
    booktitle=      "Proc. of the International Conference on Data Engineering",
    author=         "Gregory Cobena, Serge Abiteboul, Amelie Marian",
    address=        "San Jose, California, USA",
    month=          feb,
    year=           2002
}


\bibitem{XDIFF} {\sc Yuan Wang, David J. DeWitt, Jin-Yi Cai.}
X-Diff: An Effective Change Detection Algorithm for XML Documents.
